Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-23 src/1.Introduction.tex
Section 1, para 1-2

Parallel and distributed computing moved into focus at universities and teaching institutions. The interest is two-fold. Firstly, given their role, educators adapt to trends in research and industry and include parallel computing in their curricula, and secondly, parallel computing is an attractive field for department research and industry collaborations.

While industry-driven collaborations often predefine technological frameworks such as programming environments and targeted architectures, academic teaching leaves this mostly undefined. In this case, educators are exposed to a variety of solutions, approaches and trends in parallel computing. Which particular set to choose for teaching in class is not trivial. While decision factors differ, maximizing the subject relevance by teaching generic principles of parallel programming generically is among the most important ones.

>>>>

Parallel and distributed computing moved into focus at universities and teaching institutions. The interest is two-fold. Firstly, given their role, educators adapt to trends in research and industry and include parallel computing in their curricula, and secondly, parallel computing is an attractive field for department research and industry collaborations. At Sandia, we develop a performance portability library called Kokkos that is ideal for educators looking to teach parallel computing.

In teaching a class on parallel programming, educators must balance considerations of architecture, programming model, and theoretical concepts. Unfortunately, not all architectures support all programming models, nor do many programming models cleanly express all parallel programming constructs. Many vendor models compound this, requiring students have access to specific hardware, and limiting the concepts of parallelism to those supported by that architecture. This makes the choice of programming model important and difficult.
